Clicks and Cliques

### 2018-12-20 papersoul.Rnw
update moving chunk

<<life.tab, dependson=c('corplot','life'),echo=FALSE, results='asis', cache=FALSE>>=
# check correlation for prop.new.entry, should be 0.13
rho <- with(life, round(cor(CCE, prop.res),2) )

@@

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
levels(soul$Q5)[1:2] <- 'Non Response'
levels(soul$Q5)[2:6] <- 'Move from your neighborhood'
soul$Q5 <- factor(soul$Q5)

pr <- with(subset(soul, !is.na(PROJWT) ), PROJWT/3)
des.pro <- svydesign(ids=~1, strata=~QSB, weights=~pr, data=subset(soul, !is.na(PROJWT) ) )

tab <- svyby(~Q5,~CCEGRP2, des.pro, svymean,keep.var=FALSE, na.rm=T)
tab <- round(100*ftable(tab), 2)

dt <- data.frame(matrix(tab[1:9], ncol=3))
rownames(dt) <- levels(soul$Q5)
colnames(dt) <- levels(soul$CCEGRP2)
dt <- xtable(dt, caption='Willingness to move outside your neighborhood', label='move')
print(dt, caption.placement='top')

>>>>

<<life.tab, dependson=c('corplot','life'),echo=FALSE, results='asis', cache=FALSE, warning=FALSE>>=
# check correlation for prop.new.entry, should be 0.13
rho <- with(life, round(cor(CCE, prop.res),2) )

@@

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids=~1, strata=~QSB, weights=~pr, data=.) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var=FALSE, na.rm=T) %>% 
  ftable() %>% data.frame() %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption='Willingness to move outside your neighborhood', label='move') %>% 
  print(caption.placement='top')

# levels(soul$Q5)[1:2] <- 'Non Response'
# levels(soul$Q5)[2:6] <- 'Move from your neighborhood'
# soul$Q5 <- factor(soul$Q5)

# pr <- with(subset(soul, !is.na(PROJWT) ), PROJWT/3)
# des.pro <- svydesign(ids=~1, strata=~QSB, weights=~pr, data=subset(soul, !is.na(PROJWT) ) )
# tab <- svyby(~Q5,~CCEGRP2, des.pro, svymean,keep.var=FALSE, na.rm=T)
# tab <- round(100*ftable(tab), 2)
# dt <- data.frame(matrix(tab[1:9], ncol=3))
# rownames(dt) <- levels(soul$Q5)
# colnames(dt) <- levels(soul$CCEGRP2)
# dt <- xtable(dt, caption='Willingness to move outside your neighborhood', label='move')
# print(dt, caption.placement='top')
